Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-13 paper/draft1.tex
Add some future work blurbs

>>>>

\section{Future Work}

more features (this is the hardest, and most manual part, may require
domain-specific knowledge, but not necessariyly, e.g. microbenchmarking)
* features derived from micro-benchmarking \citep{wong2010demystifying}
* features derived from performance limiter analysis \citep{micikevicius2010analysis}
* more instrumentation
* more data-layout
* more threading strategies to lower latency

online distributed auto-tuning with learning, especially w/ HT-based
experiments \cite{HT} our method is indeed very well suited for parallel
explorating of multiple configurations for learning (in a cluster, e.g. in HT
context) this may get us \emph{more} than linear speed ups for better accuracy,
especially when more features will be present (see above)

interpret the learned model and confront the performance against theoreticial
(or approximated) models of mem/com/compute, arithmetic intensity, etc. to
understand performance limiters, the hardware, etc.
